---
title: "R Notebook"
output: html_notebook
---
```{r}
library(dplyr)
library(lubridate)
library(tidyverse)
library(hms)
library(chron)
library(ggplot2) 
library(GGally)
library(reshape2)
library(grid)
library(gridExtra)
library(kableExtra)
```


```{r}
d2015 <- read.csv("data/2015.csv")
d2016 <- read.csv("data/2016.csv")
d2017 <- read.csv("data/2017.csv")
d2018 <- read.csv("data/2018.csv")
d2019 <- read.csv("data/2019.csv")
```

```{r}
dataframes <- list(
  d2015,
  d2016,
  d2017,
  d2018,
  d2019
  )

csv_dataframes <- c(
  "2015.csv",
  "2016.csv",
  "2017.csv",
  "2018.csv",
  "2019.csv"
  )

number_unique = number_rows = number_variables = number_empty_rows <-c()
for (i in 1:length(dataframes)){
   number_unique <- append(number_unique, n_distinct(select(dataframes[[i]],1:1)))
   number_variables <- append(number_variables, ncol(dataframes[[i]]))
   number_rows <- append(number_rows, nrow(dataframes[[i]]))
   number_empty_rows <- append(number_empty_rows, sum(is.na(dataframes[[i]])))
}

save_summarize <- data.frame(
  number_unique,
  number_variables,
  number_rows,
  number_empty_rows
)

f_col_name <- function(data){
  paste(colnames(data),collapse = " | ")
}

#ต้องทำให้เป็น length เดียวกันก่อนเพื่อที่จะเรียงกันไป
summarize_list <- data.frame(
  name_of_files = csv_dataframes,
  variable_names = unlist(lapply(dataframes, f_col_name)),
  number_unique,
  number_variables,
  number_rows,
  number_empty_rows
)

#kabble Extra
kbl(summarize_list,"html") %>%
  kable_paper("striped", full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>% 
  column_spec(2, width = "10cm")

```

```{r}
d2015_selected <- d2015 %>% 
  add_column(year = 2015) %>% 
  add_column(Social.support = NA) %>% 
  select( year = year,
          Country = Country,
          Region = Region,
             Rank = Happiness.Rank,
             Score = Happiness.Score,
             GDP.per.capita =  Economy..GDP.per.Capita.,
             Healthy.life.expectation =  Health..Life.Expectancy. ,
             Freedom = Freedom,
             Trust.in.government =  Trust..Government.Corruption.,
             Generosity = Generosity,
              Social.support = Social.support,
              Family = Family)

d2016_selected <- d2016 %>% 
  add_column(year = 2016) %>% 
  add_column(Social.support = NA) %>% 
  select(
         year = year,
         Country = Country,
         Region = Region,
         Rank = Happiness.Rank,
         Score = Happiness.Score,
         GDP.per.capita =  Economy..GDP.per.Capita.,
         Healthy.life.expectation =  Health..Life.Expectancy. ,
         Freedom = Freedom,
         Trust.in.government =  Trust..Government.Corruption.,
         Generosity = Generosity,
         Social.support =Social.support,
         Family = Family)

d2017_selected <- d2017 %>% 
  add_column(year = 2017) %>% 
  add_column(Region = NA) %>% 
  add_column(Social.support = NA) %>% 
  select(year = year,
         Country = Country,
         Region = Region,
         Rank = Happiness.Rank,
         Score = Happiness.Score,
         GDP.per.capita =  Economy..GDP.per.Capita.,
         Healthy.life.expectation =  Health..Life.Expectancy. ,
         Freedom = Freedom,
         Trust.in.government =  Trust..Government.Corruption.,
         Generosity = Generosity,
         Social.support = Social.support,
         Family = Family)

d2018_selected <- d2018 %>% 
  add_column(year = 2018) %>% 
  add_column(Region = NA) %>% 
  add_column(Family = NA) %>% 
  select(year = year,
         Region = Region,
         Country =  Country.or.region ,
         Rank = Overall.rank ,
         Score =  Score,
         GDP.per.capita =   GDP.per.capita,
         Healthy.life.expectation =  Healthy.life.expectancy ,
         Freedom =  Freedom.to.make.life.choices ,
         Trust.in.government = Perceptions.of.corruption  ,
         Generosity = Generosity,
         Social.support = Social.support,
         Family = Family)

d2019_selected <- d2019 %>% 
  add_column(year = 2019) %>% 
  add_column(Region = NA) %>%
  add_column(Family = NA) %>% 
  select(year = year,
         Region = Region,
         Country =  Country.or.region ,
         Rank = Overall.rank ,
         Score =  Score,
         GDP.per.capita =   GDP.per.capita,
         Healthy.life.expectation =   Healthy.life.expectancy ,
         Freedom =  Freedom.to.make.life.choices ,
         Trust.in.government = Perceptions.of.corruption  ,
         Generosity = Generosity,
         Social.support = Social.support,
         Family = Family)

combined_data <- rbind(d2015_selected, 
                       d2016_selected, 
                       d2017_selected,
                       d2018_selected, 
                       d2019_selected)
```

```{r}
combined_data_list <- list(d2015_selected, 
                       d2016_selected, 
                       d2017_selected,
                       d2018_selected, 
                       d2019_selected,
                       combined_data)
combined_csv_dataframes <- c(
  "2015.csv",
  "2016.csv",
  "2017.csv",
  "2018.csv",
  "2019.csv",
  "combined_version")

number_unique = number_rows = number_variables = number_empty_rows <-c()
for (i in 1:length(combined_data_list)){
   number_unique <- append(number_unique, n_distinct(select(combined_data_list[[i]],1:1)))
   number_variables <- append(number_variables, ncol(combined_data_list[[i]]))
   number_rows <- append(number_rows, nrow(combined_data_list[[i]]))
   number_empty_rows <- append(number_empty_rows, sum(is.na(combined_data_list[[i]])))
}

combined_summarize_list <- data.frame(
  name_of_files = combined_csv_dataframes,
  variable_names = unlist(lapply(combined_data_list, f_col_name)),
  number_unique,
  number_variables,
  number_rows,
  number_empty_rows
)

kbl(combined_summarize_list,"html") %>%
  kable_paper("striped", full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>% 
  column_spec(2, width = "10cm")
```

```{r}
write.csv(combined_data,"combined_data.csv")
```

#The below is the actual one, before that is experimenting

```{r}
d2018 <- read.csv("data/2018.csv")
d2019 <- read.csv("data/2019.csv")
```

```{r}
dataframes <- list(
  d2018,
  d2019
  )

csv_dataframes <- c(
  "2018.csv",
  "2019.csv"
  )

number_unique = number_rows = number_variables = number_empty_rows <-c()
for (i in 1:length(dataframes)){
   number_unique <- append(number_unique, n_distinct(select(dataframes[[i]],1:1)))
   number_variables <- append(number_variables, ncol(dataframes[[i]]))
   number_rows <- append(number_rows, nrow(dataframes[[i]]))
   number_empty_rows <- append(number_empty_rows, sum(is.na(dataframes[[i]])))
}


f_col_name <- function(data){
  paste(colnames(data),collapse = " | ")
}

#ต้องทำให้เป็น length เดียวกันก่อนเพื่อที่จะเรียงกันไป
summarize_list <- data.frame(
  name_of_files = csv_dataframes,
  variable_names = unlist(lapply(dataframes, f_col_name)),
  number_unique,
  number_variables,
  number_rows,
  number_empty_rows
)

kbl(summarize_list,"html") %>%
  kable_paper("striped", full_width = F) 
```
```{r}
data_set <- rbind(d2018, d2019)
glimpse(data_set)
```

```{r}
data_set$Perceptions.of.corruption <- as.double(data_set$Perceptions.of.corruption)
glimpse(data_set$Perceptions.of.corruption)
```

```{r}
glimpse(data_correl)
```


```{r}
data_correl <- data_set %>% 
  select(1:9) %>% 
  drop_na
```

```{r}
library(ggplot2)
library(ggthemes)
num.cols <- sapply(data_correl, is.double)
cor.data <- cor(data_correl[,num.cols])



library(corrgram)
library(corrplot)

print(corrplot(cor.data, method = 'color'))
corrgram(data_correl)
```

The most significant factors for high happiness scores are:

* GDP per capita
* Healthy life expectancy
* Social support

GDP has the highest correlation with happiness score, and healthy life expectancy is the most significant factor for GDP per capita. However, we cannot confirm whether it is causation to one another.





